---
title: "Software"
---

### Packages in development: 

- [**hgdp**](https://github.com/Erickcufe/hgdp) a R Package with data cleaned from the Human Genome Diversity Panel (HGDP) dataset.
 
##### Human Genome Diversity Panel (HGDP) dataset 

```{r, echo=FALSE}
library(hgdp)
estudios <- hgdp::Summary_data
library(leaflet)
leaflet::leaflet() %>% 
  leaflet::addTiles() %>% 
  leaflet::addCircleMarkers(estudios$Longitude, estudios$Latitude,
                            weight = 19, radius = 2, 
                            fillOpacity = 0.9,
                            color = "darkcyan",
                            popup = paste(sep = " ", "HGDP", "<br/>",
                                          "Population:", estudios$Population,"<br/>",
                                          "Size:", estudios$n))

```


- [**seekerBio**](https://github.com/Erickcufe/seekerBio) a R package for gen/SNP search information  

```{r}
seekerBio::seeker_snp_ld_plot("rs7412")
```

- [**qualitycheck**](https://github.com/Erickcufe/qualitycheck) a R package for the organization of lots of pharmaceutical products
- Co-author of [**mxearthquakes**](https://github.com/ComunidadBioInfo/mxearthquakes) a R package that shows the data of earthquakes in Mexico from 1900 to date.

```{r}
library(mxearthquakes)
mxearthquakes::ploteq("Veracruz", 2003)
```


